Crystals

### 2017-02-12 doc/ms.tex
Minor work

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/background.pdf}
\caption{\label{fig:background}}
\end{figure}

@@

\hline
{\em Parameters}& &\\
$\sigma_0$ &    Constant noise level  &   $\ln(\sigma_0) \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln(\sigma_1) \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   LogUniform$(1, 1000)$\\
$b$       & Mean background level       & Laplace$(0, 5)$\\
$\{n_1, ..., n_4\}$  & Background deviations & iid Normal$(0,1)$\\
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & Student $t(f(x_i; \params), ,\nu)$\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{\x_1, \x_2, ..., \x_n\}$  & $\x$-values of measurements & given \\
\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}

The Laplace, or biexponential, distribution with location parameter $a$ and
scale parameter $b$ has probability density
\begin{align}
p(x | a, b) &= \frac{1}{2b}\exp\left[-\frac{|x - a|}{b}\right].
\end{align}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/background.pdf}
\caption{Three example functions showing possible shapes of the
background component.\label{fig:background}}
\end{figure}

@@

\hline
{\em Background parameters}\\
$b$       & Mean background level       & Laplace$(0, 5)$\\
$\{n_1, ..., n_4\}$  & Background deviations & iid Normal$(0,1)$\\
\hline 
{\em Noise parameters}\\
$\sigma_0$ &    Constant noise level  &   $\ln(\sigma_0) \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln(\sigma_1) \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   LogUniform$(1, 1000)$\\
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & Student-$t(f(x_i; \params), ,\nu)$\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{\x_1, \x_2, ..., \x_n\}$  & $\x$-values of measurements & given \\
\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}

The Laplace, or biexponential, distribution with location parameter
(central position) $a$ and scale parameter (width) $b$ has probability
density given by
\begin{align}
p(x | a, b) &= \frac{1}{2b}\exp\left[-\frac{|x - a|}{b}\right].
\end{align}
We used a Laplace distribution for informative priors, rather than
a more conventional normal distribution, because it assigns higher
prior probability to values far from the center, and can be computed conveniently, i.e., no special functions such as {\tt erf} are needed
to compute the cumulative distribution function.
